Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-09-10 tse19/mitigating-flakiness-speedup-table.tex
fix table

Activiti & \entry{8.46m}{2093}  & \textcolor{blue}{ 2.49x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.81x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.72x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.02x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.87x } & \textcolor{blue}{ 0\%}\\%

Apache Avro & \entry{13.65m}{3765}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

Apache Incubator Dubbo & \entry{14.33m}{2663}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

Content ExtRactor and MINEr & \entry{8.10m}{132}  & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%} & \entry{-x}{-\%}\\%

DataStax Java Driver & \entry{5.23m}{1377}  & \entry{8.30x}{1.17\%} & \entry{9.34x}{0.75\%} & \entry{9.33x}{1.15\%} & \entry{1.03x}{0\%} & \entry{6.22x}{1.41\%}\\%

DROID & \entry{6.00m}{386}  & \entry{2.32x}{15.79\%} & \entry{7.90x}{2.02\%} & \entry{4.02x}{5.33\%} & \entry{9.67x}{2.3\%} & \entry{4.76x}{6\%}\\%

Eclipse Hawkbit & \entry{17.28m}{1111}  & \entry{2.63x}{29.12\%} & \entry{2.90x}{33.22\%} & \entry{2.52x}{26.52\%} & \entry{2.49x}{9.23\%} & \entry{3.00x}{33.91\%}\\%

Facebook Linkbench & 7.16m & 98 & 1.02x & 0\% & 1.70x & 1.27\% & 1.00x & 1.00\% & 1.70x & 0.09\% & 1.69x & 0.93\%\\%

Kafka Streams & \entry{11.38m}{79}  & \entry{1.13x}{11\%} & \entry{1.02x}{0\%} & \entry{1.12x}{11.49\%} & \entry{2.63x}{1.37\%} & \entry{1.02x}{0.2\%}\\%

Rapidoid & \entry{11.68m}{476}  & \entry{1.06x}{0\%} & \entry{1.24x}{0\%} & \entry{1.10x}{0\%} & \entry{18.54x}{10.15\%} & \entry{17.17x}{9.57\%}\\%

Search Guard & \entry{13.32m}{111}  & \entry{1.78x}{0\%} & \textcolor{blue}{ 1.62x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.43x } & \textcolor{blue}{ 0\%} & \entry{2.04x}{0\%} & \entry{2.45x}{0\%}\\%

T SNE Java & \entry{6.38m}{20}  & \textcolor{blue}{ 2.02x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.22x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 1.21x } & \textcolor{blue}{ 0\%}\\%

Twilio Java & \entry{12.60m}{2529}  & \entry{1.47x}{1.37\%} & \entry{2.15x}{21\%} & \entry{3.08x}{2.18\%} & \entry{3.47x}{0\%} & \entry{2.60x}{5.54\%}\\%

Urban Airship Datacube & 11.84m & 45 & 2.31x & 20.91\% & 3.35x & 34.06\% & 1.92x & 21.46\% & 1.21x & 0\% & 2.26x & 21\%\\%

Vaadin Framework & \entry{8.97}{3683}  & \textcolor{blue}{ 2.19x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 1.91x } & \textcolor{blue}{ 0\%} & \textcolor{blue}{ 2.01x } & \textcolor{blue}{ 0\%} & \entry{1.00x}{0\%} & \textcolor{blue}{ 2.53x } & \textcolor{blue}{ 0\%}\\%

\midrule
Average & 10.42m & 1,237.86 & -x & -\% &  -x & -\%  & -x  & -\% & -x & -\% & -x & -\%\\%

>>>>

Activiti & \entry{8.46m}{2093}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Apache Avro & \entry{13.65m}{3765}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%

Apache Incubator Dubbo & \entry{14.33m}{2663}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Content ExtRactor and MINEr & \entry{8.10m}{132}  & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%

DataStax Java Driver & \entry{5.23m}{1377}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{-----}{-----} & \entry{0x}{0\%}\\%

DROID & \entry{6.00m}{386}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Eclipse Hawkbit & \entry{17.28m}{1111}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Facebook Linkbench & 7.16m & 98 & ----- & ----- & 0x & 0\% & 0x & 0\% & 0x & 0\% & 0x & 0\%\\%

Kafka Streams & \entry{11.38m}{79}  & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Rapidoid & \entry{11.68m}{476}  & \entry{-----}{-----} & \entry{-----}{-----} & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%}\\%

Search Guard & \entry{13.32m}{111}  & \entry{-----}{-----} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{-----}{-----}\\%

T SNE Java & \entry{6.38m}{20}  & \entry{1.26x}{0\%} & \entry{-----}{-----} & \entry{1.24x}{0\%} & \entry{-----}{-----} & \entry{1.23x}{0\%} \\%

Twilio Java & \entry{12.60m}{2529}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%

Urban Airship Datacube & 11.84m & 45 & 0x & 0\% & 0x & 0\% & 0x & 0\% & ----- & ----- & 0x & 0\%\\%

Vaadin Framework & \entry{8.97}{3683}  & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{0x}{0\%} & \entry{-----}{-----} & \entry{0x}{0\%}\\%

\midrule
Average & 10.42m & 1,237.86 & ----- & ----- &  ----- & -----  & -----  & ----- & ----- & ----- & ----- & ----- \\%
